---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  out.width = "100%"
)
```

# Propensity Score and Missing data
This repository contains the R scripts to reproduce the analysis workflow
of the study "__Propensity Score Analysis with partially observed baseline covariates: a practical comparison of methods for handling missing data__"
on a simulated dataset.

Before running the scripts, please install the following R packages:

``` r
install.packages(
  c("tidyverse", "BaBooN", "mice", "miceadds", "optmatch",
    "MatchIt", "WeightIt", "rms", "misaem", "twang", "CBPS", "cobalt",
    "assertive", "usethis", "here", "naniar", "tictoc", "MASS",
    "rpart", "rpart.plot", "knitr", "rmarkdown", "kableExtra",
    "gtsummary", "corrplot", "readr"), 
    dependencies = TRUE
)
```

The project contains the following folders:

- _data_, containing the R script _simultate_synthetic_dataset.R__ that
  can be used to simulate the synthetic dataset for the analysis.

- _analysis.R_, containing the R scripts _misc_functions.R_ and
  _main_analysis_. The former contains the functions that are used to
  run the analysis, the latter can be used to perform the main analysis
      
- _results.R_, containing the R markdown file _main_results.Rmd_. that
  can be used to visualize the results of the main analysis.

The analysis workflow can be reproduced as follows:

1. Run the script _data/simultate_synthetic_dataset.R_, which simulates
   the dataset and saves it in __data/synthetic_data.rds__.
   
2. Run the script _analysis/main_analysis.R_, which runs the main analysis
   and save the results.

3. Knitr the _results/main_results.Rmd_ file to produce a report of the
   results with tables and plots.
   
The workflow of the analysis is guaranteed to be reproducible with 
R version _4.1.0_ and the following packages versions:

```{r}
library(tidyverse)
library(BaBooN)
library(mice)
library(miceadds)
library(optmatch)
library(MatchIt)
library(WeightIt)
library(rms)
library(misaem)
library(twang)
library(CBPS)
library(rmarkdown)
library(knitr)
library(kableExtra)
library(gtsummary)
library(cobalt)
library(assertive)
library(usethis)
library(here)
library(naniar)
library(tictoc)
library(MASS)
library(rpart)
library(rpart.plot)
library(corrplot)
library(readr)

si <- sessionInfo()
print(si, locale = FALSE)
```
